Constructing a universe for the setoid model

### 2020-07-06 paper.tex
affiliations

\author{
  Thorsten Altenkirch \inst{1}\thanks{Supported by USAF grant FA9550-16-1-0029.}
\and
  Simon Boulier
\and
  Ambrus Kaposi \inst{2}
\and
  Christian Sattler\inst{3}\thanks{Supported by USAF grant FA9550-16-1-0029 and Swedish Research Council grant 2019-03765.}
\and
  Filippo Sestini\inst{1}
}

\institute{
  School of Computer Science, University of Nottingham, UK\\
  \email{\{psztxa,pszcs1,psxfs5\}@nottingham.ac.uk}
  \and
  E{\"o}tv{\"o}s Lor{\'a}nd University, Budapest, Hungary\\
  \email{akaposi@inf.elte.hu}
  \and
  Chalmers University of Technology, Gothenburg, Sweden
  \email{sattler@chalmers.se}
}

>>>>

\author{
  Thorsten Altenkirch \inst{1}\thanks{Supported by USAF grant FA9550-16-1-0029.}
\and
  Simon Boulier \inst{2}
\and
  Ambrus Kaposi \inst{3}\thanks{Supported by the National Research, Development and Innovation Fund of Hungary, financed under the Thematic Excellence Programme funding scheme, Project no. ED\_18-1-2019-0030 and the Bolyai Fellowship of the Hungarian Academy of Sciences, Project no.\ BO/00659/19/3.}
\and
  Christian Sattler\inst{4}\thanks{Supported by USAF grant FA9550-16-1-0029 and Swedish Research Council grant 2019-03765.}
\and
  Filippo Sestini\inst{1}
}

\institute{
  School of Computer Science, University of Nottingham, UK\\
  \email{\{psztxa,pszcs1,psxfs5\}@nottingham.ac.uk}
  \and
  Inria, Nantes, France \\
  \email{simon.boulier@inria.fr}
  \and
  E{\"o}tv{\"o}s Lor{\'a}nd University, Budapest, Hungary\\
  \email{akaposi@inf.elte.hu}
  \and
  Chalmers University of Technology, Gothenburg, Sweden
  \email{sattler@chalmers.se}
}
